---
output: rmarkdown::github_document
---

# arabia

Tools to Read 'Lowrance' Binary Track Files

## Description

Lowrance' (<http://www.lowrance.com/>) chart plotters use an ugly but straightforward binary format to encode their tracks. Tools are provided to read 'SL2' files (and, very likely 'SLG' and 'SL3' files, too).

## What's Inside The Tin

The following functions are implemented:

- `read_sl2`:	Read Lowrance binary track files
- <strike>`read_sl2_cpp`:	A "No Frills" Faster Version in C++</strike> (uncomment things in the package if you want this as the OP was having issues on Windoews with Rtools)

## Installation

```{r eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/arabia")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(arabia)
library(tidyverse)

# current verison
packageVersion("arabia")

```

### Give it a go

```{r}
system.time(xdf <- read_sl2(system.file("exdat", "example.sl2", package="arabia")))

xdf

glimpse(xdf)
```
